---
title: "Visualization mini challenge"
author: "Ethan Greenberg"
date: today
format: html
---

1.  Change the author in the yaml to your name

2.  Install the `palmerpenquins` library. Remember to comment out the install line after you have installed the library.



```{r}
#| label: installpackage 
#| install.packages("palmerpenguins")


```

3.  Load the `tidyverse` and `palmerpenguins` libraries

```{r}
#| label: loadlibraries
library(tidyverse)
library(palmerpenguins)

```

4.  Load the `penguins` dataset

```{r}
#| label: loaddata
data(penguins)

```

5.  Examine the dataset

```{r}
#| label: examinedata
head(penguins)

```

6.  Create a scatter plot of `bill_length_mm` and `bill_depth_mm` with `species` as the color and having the point shape be `sex`. Define the shapes and colors using `scale_color_manual` and `scale_shape_manual`. Size of the points should 3.

```{r}
#| label: theplot
ggplot(data=penguins)+
    geom_point(aes(x=bill_length_mm,y = bill_depth_mm,color=species,shape=sex),size=3)+
    scale_color_manual(values = c("Adelie" = "lightblue","Chinstrap"="magenta","Gentoo"="red")) +
    scale_shape_manual(values = c("male" = 15,"female"= 17,"NA"=18)) +
    labs(x = "Bil length (mm)",y="Bill depth (mm)",title="Bill length and depth of Palmer penguins") +
    theme_classic()+
    theme(axis.text=element_text(size=14),
          axis.title=element_text(size = 20),
          plot.title=element_text(size=24,hjust=0.5),
          legend.text = element_text(size=14),
          legend.title = element_text(size = 20)
          )


```
